---
title: "Assignment4"
author: "\"
date: "10/25/2021"
output: html_document
---

## Question 3

# a)
```{r}
library("ISLR")
library(boot)
set.seed(1)
cv.error=rep(0,10)
for (i in 1:10){
glm.fit=glm(wage ~ poly(age ,i),data=Wage)
cv.error[i]=cv.glm(Wage,glm.fit, K = 10)$delta[2]
}
cv.error

plot(1:10, cv.error, xlab = "Degree of the Polynomial", ylab = "CV error", type = "l")
```

According to the Cross Validation Error for different polynomials, degree 3 or 4 could be choosen.

```{r}
fit.1 = lm(wage~poly(age, 1), data=Wage)
fit.2 = lm(wage~poly(age, 2), data=Wage)
fit.3 = lm(wage~poly(age, 3), data=Wage)
fit.4 = lm(wage~poly(age, 4), data=Wage)
fit.5 = lm(wage~poly(age, 5), data=Wage)
fit.6 = lm(wage~poly(age, 6), data=Wage)
fit.7 = lm(wage~poly(age, 7), data=Wage)
fit.8 = lm(wage~poly(age, 8), data=Wage)
fit.9 = lm(wage~poly(age, 9), data=Wage)
fit.10 = lm(wage~poly(age, 10), data=Wage)
anova(fit.1, fit.2, fit.3, fit.4, fit.5, fit.6, fit.7, fit.8, fit.9, fit.10)

```

According to the anova function, polynomials of degree 3 and 2 are significant at 0.01 level, and polynomial of degree 4 is significant at 0.1 level.

Considering the result from cross validation method and anova function, we would choose the polynomial with degree 3.

```{r}
plot(wage ~ age, data = Wage, col = "grey")
agelims = range(Wage$age)
age.grid = seq(from=agelims[1], to=agelims[2])
lm.pred = predict(fit.3, data.frame(age=age.grid))
lines(age.grid, lm.pred, col="blue", lwd=2)
```
 
# b)
```{r}
cut.cv = rep(NA, 10)
for(i in 2:10){
  Wage$age.cut = cut(Wage$age,i)
  fit= glm(wage ~ age.cut, data = Wage)
  cut.cv[i] = cv.glm(Wage, fit, K =10)$delta[2]
}
plot(2:10,cut.cv[2:10], type = "l")
```

The Cross Validation methods gives the smallest error when there are 8 cuts. 

```{r}
plot(wage~age, data = Wage, col="grey")
glm.fit = glm(wage~ cut(age,8), data = Wage)
step_predict = predict(glm.fit,data.frame(age=age.grid))

lines(age.grid, step_predict, type = "l", col = "red")
```

## Question 4

# a)
```{r}
library(MASS)
lm.fit = lm(nox ~ poly(dis,3) , data = Boston)
dislims = range(Boston$dis)
dis.grid = seq(from=dislims[1], to=dislims[2], by = 0.1)
lm.pred = predict(lm.fit, data.frame(dis = dis.grid))
plot(nox ~ dis, data = Boston, col = "grey")
lines(dis.grid, lm.pred, col = "red", lwd = 2)
```

# b)
```{r}
fit.1 = lm(nox~poly(dis, 1), data=Boston)
fit.2 = lm(nox~poly(dis, 2), data=Boston)
fit.3 = lm(nox~poly(dis, 3), data=Boston)
fit.4 = lm(nox~poly(dis, 4), data=Boston)
fit.5 = lm(nox~poly(dis, 5), data=Boston)
fit.6 = lm(nox~poly(dis, 6), data=Boston)
fit.7 = lm(nox~poly(dis, 7), data=Boston)
fit.8 = lm(nox~poly(dis, 8), data=Boston)
fit.9 = lm(nox~poly(dis, 9), data=Boston)
fit.10 = lm(nox~poly(dis, 10), data=Boston)
anova(fit.1, fit.2, fit.3, fit.4, fit.5, fit.6, fit.7, fit.8, fit.9, fit.10)

```

# c)
```{r}
library(MASS)
library(boot)
all.deltas = rep(NA, 10)
for (i in 1:10) {
    glm.fit = glm(nox ~ poly(dis, i), data = Boston)
    all.deltas[i] = cv.glm(Boston, glm.fit, K = 10)$delta[2]
}
plot(1:10, all.deltas, xlab = "degree of polynomial", ylab = "CV error", type = "l")
```

The Cross Validation methods gives the smallest error when the degree is 4.

# d)
```{r}
library(splines)
attach(Boston)
attr(bs(Boston$dis, df = 4), "knots")
lm.fit = lm(nox ~ bs(dis, df= 4), data = Boston)
dislims = range(Boston$dis)
dis.grid = seq(from=dislims[1], to=dislims[2], by = 0.1)
lm.pred = predict(lm.fit, list(dis = dis.grid))
plot(nox ~ dis, data = Boston, col = "grey")
lines(dis.grid, lm.pred, col = "red", lwd = 2)
``` 

Using bs() function, the knot was automatically generated. There is one knot with 4 degrees of freedom, and the knot is the median of the "dis".

# e)
```{r}

rss = rep(NA, 14)

for (i in 4:14) {
  fit = lm(nox ~ bs(dis,i), data = Boston)
  rss[i] = sum(fit$residuals^2)
}
rss[c(-1,-2,-3)]

```

# f)
```{r}
cv.error = rep(NA, 14)

for (i in 4:14) {
  fit = glm(nox ~ bs(dis,i), data = Boston)
  cv.error[i] = cv.glm(Boston, fit, K = 10)$delta[2]
}

plot(4:14, cv.error[c(-1,-2,-3)], xlab = "degrees of regression spline", ylab = "CV error", type = "l")

```
