---
title: "Stat 3301: Homework 7"
date: "Xidan Kou (kou.55)"
author: "Due Thursday, October 22 by 11:59pm EDT"
output: html_document
---

Setup:
```{r message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(tidyverse)
```

##### Solution to Question 1

```{r, echo = FALSE, message = FALSE}
library(readr)
nba <- read_csv("~/Desktop/Stat 3301/nbahtwt.csv")
guards = nba %>% filter(pos == "G")
guards.mod = lm(wt ~ ht + age, data = guards)
summary(guards.mod)
```


(a) 
```{r}
X = model.matrix(guards.mod)
(sig2hat = summary(guards.mod)$sigma^2)
coeMatrix = sig2hat * solve(t(X)%*%X)
print(coeMatrix)
vcov(guards.mod)
```


(b) Use your result from part (a) to calculate the standard error for the estimated coefficient for the
regressor `ht`. Verify your answer by comparing it with the summary of the fitted regression model 
displayed above.
```{r}
sqrt(diag(coeMatrix))
summary(guards.mod)$coefficients
```

(c) 
Answer: For NBA guards in same age, one additional inch increase in height results expected weight increase of 4.4250 pounds. 

(d) 
Answer:
$H_0$ :  $\beta_2 = 0$ 
$H_1$ :  $\beta_2 \neq 0$
```{r}
p = 2*pt(-2.072,199)
print(p)
```
We have p value = 0.039, which p value < 0.05. So, We reject the null hypothesis and conclude that adding `age` to the model that uses `height` to predict `weight` is useful.

(e) 
```{r}
XtXinv = solve(t(X)%*%X)
xstar = matrix(c(1, 78.5, 20),ncol = 1)
sig = summary(guards.mod)$sigma
tmp = sqrt(t(xstar)%*%XtXinv%*%xstar)
setfit = sig*tmp
print(setfit)
predict(guards.mod, newdata = data.frame(ht = 78.5,  age = 20),interval = "confidence", se.fit = TRUE)

```

(f) 
```{r}
CI = (-148.8193632 +4.425*78.5 + 0.4145856*20)+ c(-1,1)*qt(0.95, df = 199)*c(setfit)
print(CI)
predict(guards.mod, newdata = data.frame(ht = 78.5,  age = 20),interval = "confidence", level = 0.9)

```
We are 90% confidence that the range of average weight for NBA guards who are 20-year-old and  78.5" tall is between 203.958 pounds and 209.7151 pounds. 
