---
title: "XidanKou_HW2"
author: "Xidan Kou"
date: "2/2/2021"
output: html_document
---

##Question 1

a)
```{r}
hiroshima <- read.table("~/Desktop/Stat 3302/hiroshima.txt",header = TRUE)
hiroshima$proportion = hiroshima$leukemia / (hiroshima$leukemia + hiroshima$other + hiroshima$total)

plot(hiroshima$midpoint, jitter(hiroshima$proportion), ylab = "Proportion of total cancer deaths that are due to Leukemia", xlab = "Midpoint of radiation exposure")
```

The graph suggests that as the radiation received increases, the proportion of total cancer deaths that are due to Leukemia increases as well.

b)
```{r}

VTM = function(vc,dm){
  matrix(vc,ncol = length(vc),nrow = dm,byrow = TRUE)
}

data.death = data.frame()
for(j in 1:nrow(hiroshima)){
  
new.line = c(hiroshima$midpoint[j],1)
new.chunk = VTM(new.line,hiroshima$leukemia[j])
data.death = rbind(data.death,new.chunk)

new.0s = c(hiroshima$midpoint[j], 0)
new.chunk = VTM(new.0s,(hiroshima$other[j]))
data.death = rbind(data.death,new.chunk)

}
colnames(data.death) = c("radiation_midpoint", "leukemia_dead")
head(data.death)

model = glm(leukemia_dead ~ radiation_midpoint, data = data.death, family = "binomial" )
summary(model)

temp = summary(model)$coefficients
beta.point.estimated = temp["radiation_midpoint","Estimate"]

beta.ci = c(temp["radiation_midpoint","Estimate"]- 1.96*temp["radiation_midpoint","Std. Error"], temp["radiation_midpoint","Estimate"]+ 1.96*temp["radiation_midpoint","Std. Error"])


OR.est = exp(beta.point.estimated)
OR.est
OR.ci = exp(beta.ci)
OR.ci

```

For each one level increase in radiation, the odds of cancer deaths that are due to leukemia increase 1.012 times(95% Confidence Interval of odds of $\beta_1$ is (1.008749,10014644)).

##Question 2
 
a)

$Y_i$(i = 1,...,n) are n independent Bern($P_i$) RVs. 

$Y_i$ = 1 if the person experienced a sore throat
      = 0 if the person does not experienced a sore throat
   
$x_i$ = duration of the surgery in minute 

model : expit{$\beta_0$ + $\beta_ix_i$ }

b)
```{r}
throat <- read.table("~/Desktop/Stat 3302/throat.txt",header = TRUE)
model_throat = glm(throat ~ duration, data = throat, family = "binomial")
summary(model_throat)

temp = summary(model_throat)$coefficients
beta.point.estimated = temp["duration","Estimate"]

beta.ci = c(temp["duration","Estimate"]- 1.96*temp["duration","Std. Error"], temp["duration","Estimate"]+ 1.96*temp["duration","Std. Error"])


OR.est = exp(beta.point.estimated)
OR.est
OR.ci = exp(beta.ci)
OR.ci


```

For each one minute increase in duration of the surgery, the odds of experience a sore throat increase 1.075 times(95% Confidence Interval of odds of $\beta_1$ is (1.022394, 1.129644)).









