---
title: "Stat 3301: Homework 6"
date: "Xidan Kou (kou.55)"
author: "Due Thursday, October 15 by 11:59pm EDT"
output: html_document
---


\


Setup:
```{r message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(tidyverse)
library(patchwork)
library(broom)
```
##### Solution to Question 1
(a) Make a scatterplot matrix for the variables `ht`, `age` and `wt`. Use the plots to describe the pairwise relationships between the variables.
```{r}
library(readr)
nba <- read_csv("~/Desktop/Stat 3301/nbahtwt.csv")
guards = subset(nba,pos=="G")
pairs(~wt+ht+age,data = guards)
```

Answer: It seems weight and age does not have any obvious trend. Weight and height has positive linear relationship, which is as height increase, weight increase. 

(b) Use `R` to fit a multiple linear regression model with mean function $E(\mathtt{wt} \mid
\mathtt{ht}, \mathtt{age}) = \beta_0 + \beta_1 \mathtt{ht} + \beta_2 \mathtt{age}$ and
variance function $\mbox{Var}(\mathtt{wt} \mid \mathtt{ht}, \mathtt{age}) = \sigma^2$.
Use the `summary` function to display `R`'s standard summary of the fitted model.
```{r}
nba.lm = lm(wt ~ ht + age, data = guards)
summary(nba.lm)$r.squared
```

Answer:
R^2 = 0.39824.

(c) Report the numeric values of the parameter estimates $\hat{\beta}_j$, $j = 0, 1, 2$, 
and $\hat{\sigma}^2$.
```{r}
summary(nba.lm)$coefficients
summary(nba.lm)$sigma^2
```

Answer:
$\beta_0$ is -148.819, $\beta_1$ is 4.425 and $\beta_2$ is 0.415.
$\hat{\sigma}^2$ = 142.971
$E(\mathtt{ht}, \mathtt{age}) = -148.8194 + 4.425 \mathtt{ht} + 0.414 \mathtt{age}$

(d) Report the numeric value of the degrees of freedom associated with the fitted model. Say what
formula you use to calculate this value.

Answer: df = n-p-1 = 202-3-1 = 198.

(e) Use R to compute and display the 3x3 matrix $X^T X$, where *X* is the $202 \times 3$ matrix used to fit the regression model.
```{r}
Y = matrix(guards$wt,ncol = 1)
X = cbind(rep(1,length(Y)),guards$ht,guards$age)
tx_x = t(X)%*%X
print(tx_x)
```

(f) Use R to compute and report the 3x3 matrix $(X^TX)^{-1}$.
```{r}
solve(tx_x)
```

(g) Nate Robinson should be the first case in the data set ($i = 1$). Compute and report 
the leverage $h_{11}$ for Nate Robinson under this MLR model in two ways: (i) using the 
`hatvalues` function and (ii) by computing the **H** matrix directly and reporting the 
first diagonal element.
```{r}
head(hatvalues(nba.lm),11)
H = X%*%solve(t(X)%*%X)%*%t(X)
head(diag(H),11)
```

Answer: $h_{11}$ =0.0239.

(h) Make three plots of the standardized residuals $r_i$: (i) $r_i$ versus the fitted values
$\hat{y}_i$, (ii) $r_i$ versus `ht` and (iii) $r_i$ versus `age`. Do the plots suggest any
problems with our assumptions about the mean and variance functions?

```{r}
rsd = rstandard(nba.lm)
base = augment(nba.lm) %>% ggplot(aes(y = rsd)) + geom_point() + geom_hline(yintercept = 0) +
  theme_bw(20) + ylim(-0.5, .5) + ylab("standard residuals")

(base + aes(x = .fitted) + xlab("fitted values")) / ((base + aes(x = ht) + xlab("height")) +
  (base + aes(x = age)))

```

Answer:It does suggest the variance function, and proved the constant variance assumption in this case, because there are no obvious trend of the three plots. 
