---
title: "Stat 3301: Homework 8"
date: "Xidan Kou (kou.55)"
author: "Due Thursday, October 29 by 11:59pm EDT"
output: html_document
---


Setup:
```{r message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(tidyverse)
```
##### Solution to Question 1

(a)

```{r}
data("UN11")
boxplot(log(ppgdp) ~ group, ylab = "log(ppgdp)",xlab = "group",data = UN11)
```

(b) 
```{r}
UN11$Uoecd = as.numeric(UN11$group == "oecd")
UN11$Uafica = as.numeric(UN11$group == "africa")
```

(c) 
```{r}
log_ppgdp_lm = summary(lm(log(ppgdp) ~ Uoecd + Uafica, data = UN11))
log_ppgdp_lm$sigma^2
log_ppgdp_lm$coefficients
```

Answer: $\hat{\beta}_0$ is 8.60,  $\hat{\beta}_1$ is 1.76, $\hat{\beta}_2$ is -1.54.
 $\hat{\sigma}^2$ is 1.334.

(d) 
Answer: $\hat{\beta}_0$ means the mean log per person gdp for `other` countries.
        $\hat{\beta}_1$ means the difference in average log per person gdp between          `oecd` countries and `other` countries.
        $\hat{\beta}_2$ means the difference in average log per person gdp between          `africa` countries and `other` countries.

(e)  
$$\hat{E}(\mathtt{log(ppgdp)} \mid 
\mathtt{group} = \mathtt{oecd}) = \hat{\beta}_0 + \hat{\beta}_1 = 8.60 + 1.76 = 10.36$$ 

(f) 
$\hat{E}(\mathtt{log(ppgdp)} \mid \mathtt{group} = \mathtt{oecd}) -\hat{E}(\mathtt{log(ppgdp)} \mid \mathtt{group} = \mathtt{africa}) = \hat{\beta}_0+\hat{\beta}_1 - (\hat{\beta}_0 + \hat{\beta}_2) = \hat{\beta}_1-\hat{\beta}_2 = 1.76+1.54 = 3.3$.


(g) 
```{r eval = FALSE}
lm(log(ppgdp) ~ group, data = UN11)
```

$$
  \log(\mathtt{ppgdp}_i) = \beta_0 + \beta_1 U_{other, i} + \beta_2 U_{africa, i} + e_i,
$$
where $e_i \stackrel{\mathrm{iid}}{\sim} \mbox{N}(0, \sigma^2)$ 

