---
title: "Stat 3301: Homework 9"
date: "Xidan Kou (kou.55)"
author: "Due Thursday, November 19 by 11:59pm EST"
output: html_document
---

Setup:
```{r message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(tidyverse)
```

#### Answer to Question 1

(a) 
```{r} 
nhl <- read_csv("~/Desktop/Stat 3301/nhlfans.csv")
summary( lm( log(tts) ~ log(estFans) * country, data=nhl ) )

p = nhl %>% ggplot(aes(x =log(estFans) , y = log(tts)))  + geom_point(aes(color = country))+ geom_smooth(aes(color = country), method = "lm") 
p + theme_bw(20) + xlab("log(estFans)") + ylab("log(tts)") + scale_color_hue("Country")
```

Regression equation for Interaction Model:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ \beta_2 U_{\mathtt{USA}_i} + \beta_3 U_{\mathtt{USA}_i} log(estFan)_i+ e_i.
$$

Regression equation for terms in USA:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ \beta_2 + \beta_3 log(estFan)_i+ e_i.
$$

Regression equation for terms in Canada:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ e_i.
$$

(b) 
```{r}
summary( lm( log(tts) ~ log(estFans) + country, data=nhl ))

modMain = lm( log(tts) ~ log(estFans) + country, data=nhl )
library(broom)
ggplot(augment(modMain),aes(x= log(nhl$estFans), y=log(nhl$tts), color=country)) + geom_jitter(height = 0.5,width = 0,alpha=0.5)+ geom_line(aes(y = .fitted, group = country), size = 1) + theme_bw(22) + xlab("log(estFans)") + ylab("log(tts)")

```

Regression equation for Main Effects Model:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ \beta_2 U_{\mathtt{USA}_i} + e_i.
$$

Regression equation for terms in USA:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ \beta_2 + e_i.
$$

Regression equation for terms in Canada:
$$
  \log (tts)_i = \beta_0 +\beta_1 log(estFan)_i+ e_i.
$$

(c) 
The Model (`log(ttsm) ~ log(estFans)`) would be sufficient to describe the relationship between variables. The p value for interaction term in model (`log(ttsm) ~ country*log(estFans)`) is 0.1898, so we say the model without the interaction term would be sufficient to describe the relationship. The p value for variable country in model (`log(ttsm) ~ country + log(estFans)`) is 0.965, , so we say the model without the country variable would be sufficient to describe the relationship. Thus, The Model (`log(ttsm) ~ log(estFans)`) would be the best in this case and also sufficient.


#### Answer to Question 2

(a) 
```{r}
Rateprof %>% ggplot(aes(y = quality, x = gender, color = discipline)) + geom_boxplot()
```

(b) 
$$
  E(\mathtt{quality} | X) = \beta_0 +\beta_1 U_{\mathtt{male}_i} + \beta_2 U_{\mathtt{SocSci}_i} + \beta_3 U_{\mathtt{STEM}_i}
    + \beta_4 U_{\mathtt{Pre-prof}_i} +  \beta_5 U_{\mathtt{SocSci}_i}U_{\mathtt{male}_i} + \beta_6 U_{\mathtt{STEM}_i} U_{\mathtt{male}_i} + \beta_7 U_{\mathtt{Pre-prf}_i} U_{\mathtt{male}_i} + e_i.
$$

```{r}
summary(lm(quality ~ gender*discipline, data = Rateprof))
```

(c) 
The intercept $\beta_0$ is the Sample average quality for female instructor and Humanities course.

(d) 
```{r}
vcov(lm(quality ~ gender*discipline, data = Rateprof))
se = sqrt(0.03617642 + 0.05646494 - (2*0.03617642))
(-0.08316-0.01961) + c(-1,1)*qt(0.975,358)*se
```

\[
  \hat{E}(quality \mid male, STEM) - \hat{E}(quality \mid male, Hum) =(\hat{\beta_0} +\hat{\beta_1}+\hat{\beta_3}+\hat{\beta_6})-(\hat{\beta_0} +\hat{\beta_1}) = \hat{\beta_3}+\hat{\beta_6} = -0.08316 -0.01961 = -0.10277.
\]

CI : \[
  \hat{E}(quality \mid male, STEM) - \hat{E}(quality \mid male, Hum) \pm t(0.975,358)\hat{se}(\hat{\beta_3}+\hat{\beta_6}) = (-0.3828899,0.1773499).
\]
